### 2015-08-23 output/table_compare_classalg.tex
Add LICENSE

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Evaluation of different classification algorithms}}
\label{table:table_compare_classalg}
\begin{tabular}{rlllllllll}
\toprule 
 & \textbf{Algorithm1} & \textbf{automat} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
Accuracy & 0.78 & 0.79 & 0.78 & 0.76 & 0.24 & & & &  \tabularnewline 
Precision & 0.53 & 0.56 & 0.57 & NaN & 0.24 & & & &  \tabularnewline 
Recall & 0.69 & 0.56 & 0.29 & 0.00 & 1.00 & & & &  \tabularnewline 
F-measure & 0.60 & 0.56 & 0.38 & NaN & 0.39 & & & &  \tabularnewline 
AUC & 0.75 & 0.71 & 0.61 & 0.50 & 0.50 & & & &  \tabularnewline 
MCC & 0.45 & 0.42 & 0.28 & NaN & NaN & & & &  \tabularnewline 
Number "Yes" & 137 & 106 & 53 & 0 & 438 & & & &  \tabularnewline 
\bottomrule 
\end{tabular} 
\begin{tablenotes}
\small
\item\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent. \item Algorithm1: (anywhere in patent:) ``automat" OR ``robot" OR ``movable arm" OR ``autonomous" OR  ``adaptive" OR ``self-generat" OR (in title + abstract:) ``detect" OR ``program" OR ``computer".
\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
\item AUC: Area under (the receiver operating) curve.
\item MCC: Matthew's correlation coefficient.
\item\textit{Source:} USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}

>>>>

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Evaluation of different classification algorithms}}
\label{table:table_compare_classalg}
\begin{tabular}{rlllllllll}
\toprule 
 & \textbf{Algorithm1} & \textbf{automat} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
Accuracy & 0.79 & 0.79 & 0.78 & 0.76 & 0.24 & & & &  \tabularnewline 
Precision & 0.55 & 0.56 & 0.57 & NaN & 0.24 & & & &  \tabularnewline 
Recall & 0.66 & 0.56 & 0.29 & 0.00 & 1.00 & & & &  \tabularnewline 
F-measure & 0.60 & 0.56 & 0.38 & NaN & 0.39 & & & &  \tabularnewline 
AUC & 0.74 & 0.71 & 0.61 & 0.50 & 0.50 & & & &  \tabularnewline 
MCC & 0.46 & 0.42 & 0.28 & NaN & NaN & & & &  \tabularnewline 
Number "Yes" & 125 & 106 & 53 & 0 & 438 & & & &  \tabularnewline 
\bottomrule 
\end{tabular} 
\begin{tablenotes}
\small
\item\textit{Note:} Classified as automation patents if at least one match of keywords in all parts of patent. \item Algorithm1: (anywhere in patent:) ``automat" OR ``robot" OR ``movable arm" OR ``autonomous" OR  ``adaptive" OR ``self-generat" OR (in title + abstract:) ``detect" OR ``program" OR ``computer".
\item Bessen-Hunt: (anywhere in patent:) ``software" OR (``computer" AND ``program") ANDNOT ((in title:) ``chip" OR ``semiconductor" OR ``bus" OR ``circuit" OR ``circuitry") ANDNOT ((anwhere in patent:) ``antigen" OR ``antigenic" OR ``chromatography").
\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
\item AUC: Area under (the receiver operating) curve.
\item MCC: Matthew's correlation coefficient.
\item\textit{Source:} USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}

### 2015-08-23 output/table_meancorr_laborm_patentm.tex
Add LICENSE

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Average correlations of labor market outcomes and automation across industries}}
\label{tab:meancorr_laborm_patentm}
\begin{tabular}{lrrrrrrrrrr}
\toprule \addlinespace[0.5em]
 & \rot{Employment} & \rot{Employment share} &  \rot{Capital productivity} & \rot{Output} & \rot{Capital cost} &  \rot{Labor cost} & \rot{Output deflator} & \rot{Production} & \rot{Capital} & \rot{Labor productivity} \tabularnewline[0.05cm]
\midrule \addlinespace[0.5em]
\# Automation patents$^1$ & \textbf{-0.51} & -0.02 & 0.02 & 0.38 & 0.35 & 0.47 & \textbf{0.46} & \textbf{0.51} & \textbf{0.63} & \textbf{0.72}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.44)}} & \scriptsize{\scriptsize{(0.44)}} & \scriptsize{(0.39)} & \scriptsize{(0.60)} & \scriptsize{(0.43)} & \scriptsize{(0.48)} & \scriptsize{(0.23)} & \scriptsize{(0.37)} & \scriptsize{(0.62)} & \scriptsize{(0.63)} \tabularnewline[0.1cm]
Average match per patent & \textbf{-0.57} & 0 & 0.09 & 0.31 & 0.38 & 0.44 & \textbf{0.51} & \textbf{0.53} & 0.54 & \textbf{0.74}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{(0.38)} & \scriptsize{(0.50)} & \scriptsize{(0.45)} & \scriptsize{(0.52)} & \scriptsize{(0.24)} & \scriptsize{(0.31)} & \scriptsize{(0.62)} & \scriptsize{(0.68)} \tabularnewline[0.1cm]
Share of automation patents & \textbf{-0.61} & -0.01 & 0.13 & 0.37 & 0.43 & \textbf{0.53} & \textbf{0.57} & \textbf{0.63} & 0.61 & \textbf{0.83}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.41)} & \scriptsize{(0.55)} & \scriptsize{(0.45)} & \scriptsize{(0.50)} & \scriptsize{(0.17)} & \scriptsize{(0.35)} & \scriptsize{(0.67)} & \scriptsize{(0.72)} \tabularnewline[0.1cm]
Automation index$^2$ & \textbf{-0.57} & 0 & 0.09 & 0.31 & 0.38 & 0.44 & \textbf{0.51} & \textbf{0.53} & 0.54 & \textbf{0.74}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{(0.38)} & \scriptsize{(0.50)} & \scriptsize{(0.45)} & \scriptsize{(0.52)} & \scriptsize{(0.24)} & \scriptsize{(0.31)} & \scriptsize{(0.62)} & \scriptsize{(0.68)} \tabularnewline[0.1cm]
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item \textit{Note:} Correlations are calculated from the yearly time series 1987-2014 of the automation indicator and the labor market outcome series. The values are cross-sectional averages across the 26 manufacturing industries. Values in parentheses show standard deviations. Bold values are at least one standard deviation away from 0.
\item $^1$: Automation patents are defined as patents with at least one keyword match.
\item $^2$: Calculated as $log(1 + \text{number of matches per patent})$.
\item \textit{Source:} BLS, USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}

>>>>

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Average correlations of labor market outcomes and automation across industries}}
\label{tab:meancorr_laborm_patentm}
\begin{tabular}{lrrrrrrrrrr}
\toprule \addlinespace[0.5em]
 & \rot{Employment} & \rot{Employment share} &  \rot{Capital productivity} & \rot{Output} & \rot{Capital cost} &  \rot{Labor cost} & \rot{Output deflator} & \rot{Production} & \rot{Capital} & \rot{Labor productivity} \tabularnewline[0.05cm]
\midrule \addlinespace[0.5em]
\# Automation patents$^1$ & \textbf{-0.56} & -0.02 & 0.04 & 0.36 & 0.35 & 0.46 & \textbf{0.49} & \textbf{0.52} & 0.6 & \textbf{0.76}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{\scriptsize{(0.46)}} & \scriptsize{(0.41)} & \scriptsize{(0.59)} & \scriptsize{(0.44)} & \scriptsize{(0.50)} & \scriptsize{(0.23)} & \scriptsize{(0.38)} & \scriptsize{(0.62)} & \scriptsize{(0.65)} \tabularnewline[0.1cm]
Average match per patent & \textbf{-0.59} & 0 & 0.1 & 0.33 & 0.4 & 0.46 & \textbf{0.52} & \textbf{0.55} & 0.56 & \textbf{0.77}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.38)} & \scriptsize{(0.51)} & \scriptsize{(0.44)} & \scriptsize{(0.52)} & \scriptsize{(0.21)} & \scriptsize{(0.32)} & \scriptsize{(0.63)} & \scriptsize{(0.69)} \tabularnewline[0.1cm]
Share of automation patents & \textbf{-0.67} & -0.02 & 0.14 & 0.34 & 0.4 & 0.48 & \textbf{0.59} & \textbf{0.6} & 0.55 & \textbf{0.87}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.49)}} & \scriptsize{\scriptsize{(0.52)}} & \scriptsize{(0.44)} & \scriptsize{(0.53)} & \scriptsize{(0.45)} & \scriptsize{(0.53)} & \scriptsize{(0.17)} & \scriptsize{(0.37)} & \scriptsize{(0.66)} & \scriptsize{(0.74)} \tabularnewline[0.1cm]
Automation index$^2$ & \textbf{-0.59} & 0 & 0.1 & 0.33 & 0.4 & 0.46 & \textbf{0.52} & \textbf{0.55} & 0.56 & \textbf{0.77}  \tabularnewline[0.0cm]
 & \scriptsize{\scriptsize{(0.48)}} & \scriptsize{\scriptsize{(0.50)}} & \scriptsize{(0.38)} & \scriptsize{(0.51)} & \scriptsize{(0.44)} & \scriptsize{(0.52)} & \scriptsize{(0.21)} & \scriptsize{(0.32)} & \scriptsize{(0.63)} & \scriptsize{(0.69)} \tabularnewline[0.1cm]
\bottomrule
\end{tabular}
\begin{tablenotes}
\small
\item \textit{Note:} Correlations are calculated from the yearly time series 1987-2014 of the automation indicator and the labor market outcome series. The values are cross-sectional averages across the 26 manufacturing industries. Values in parentheses show standard deviations. Bold values are at least one standard deviation away from 0.
\item $^1$: Automation patents are defined as patents with at least one keyword match.
\item $^2$: Calculated as $log(1 + \text{number of matches per patent})$.
\item \textit{Source:} BLS, USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}
